% Use document class "aletter.cls" (for letters):
\documentclass[11pt, oneside]{essay}

% ISO 8859-1 character encoding is assumed
\usepackage[finnish, english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{color}
\usepackage{amsmath, amssymb}

\newcommand{\tred}[1]{\textcolor{red}{#1}}

\title{List of Publications}
\author{KyungHyun Cho}

\begin{document}

\maketitle

\vspace{5mm}

\section{Journals}

\textbf{Kyunghyun Cho}, Tapani Raiko and Alexander Ilin. Enhanced
Gradient for Training Restricted Boltzmann Machines. Neural
Computation, Volume 25 Issue 3 Pages 805--831, March 2013.

\section{Conference Proceedings}

\subsection{Deep Learning: Boltzmann Machines}

\textbf{Kyunghyun Cho}, Tapani Raiko and Alexander Ilin. Enhanced
Gradient and Adaptive Learning Rate for Training
Restricted Boltzmann Machines. In Proceedings of the 28th
International Conference on Machine Learning (ICML 2011),
pages 105--112, June 2011.

\textbf{Kyunghyun Cho}, Tapani Raiko and Alexander Ilin. Parallel
Tempering is Efficient for Learning Restricted Boltzmann
Machines. In Proceedings of the 2010 International Joint
Conference on Neural Networks (IJCNN 2010), pages 1--8, July
2010.

\textbf{Kyunghyun Cho}, Alexander Ilin and Tapani Raiko.
Tikhonov-Type Regularization for Restricted Boltzmann
Machines. In Proceedings of the 22nd International
Conference on Artificial Neural Networks (ICANN 2012), pages
81--88, September 2012.

\textbf{Kyunghyun Cho}, Alexander Ilin and Tapani Raiko. Improved
Learning of Gaussian- Bernoulli Restricted Boltzmann
Machines. In Proceedings of the 21st International
Conference on Artificial Neural Networks (ICANN 2011), pages
10--17, June 2011.

\textbf{Kyunghyun Cho}, Tapani Raiko and Alexander Ilin.
Gaussian-Bernoulli Deep Boltzmann Machines. In Proceedings
of the 2013 International Joint Conference on Neural
Networks (IJCNN 2013), August 2013.

\textbf{Kyunghyun Cho}, Tapani Raiko, Alexander Ilin and Juha
Karhunen. A Two-Stage Pretraining Algorithm for Deep
Boltzmann Machines. In Proceedings of the 23rd International
Conference on Artificial Neural Networks (ICANN 2013),
September 2013.



\subsection{Deep Learning: Feedforward Neural Networks}

\textbf{Kyunghyun Cho}. Simple Sparsification Improves Sparse
Denoising Autoencoders in Denoising Highly Corrupted Images.
In Proceedings of the 30th International Conference on
Machine Learning (ICML 2013), pages 432--440, June 2013.

Caglar Gulcehre, \textbf{Kyunghyun Cho}, Razvan Pascanu and Yoshua Bengio.
Learned-norm pooling for deep neural networks. 
In Proceedings of the International Conference on Artificial
Intelligence and Statistics. Apr 2014. (\textit{submitted})

Hannes Schulz, \textbf{Kyunghyun Cho}, Tapani Raiko and Sven Behnke.
Two-Layer Contractive Encodings with Linear Transformation
of Perceptrons for Semi-Supervised Learning. 
In Proceedings of the International Conference on Neural
Information Processing (ICONIP 2013), pages 450--457, Nov 2013.

\textbf{Kyunghyun Cho}.
Understanding Dropout: Training Multi-Layer Perceptrons with
Auxiliary Independent Stochastic Neurons. 
In Proceedings of the International Conference on Neural
Information Processing (ICONIP 2013), pages 474--481, Nov 2013.


\subsection{Applications}

\textbf{Kyunghyun Cho} and Xi Chen.  Classifying and
Visualizing Motion Capture Sequences using Deep Neural
Networks.  In Proceedings of the International Conference on
Computer Vision Theory and Applications (VISAPP 2014), Jan
2014, (\textit{to appear})

\textbf{Kyunghyun Cho}. Boltzmann Machines for Image Denoising. In
Proceedings of the 23rd International Conference on
Artificial Neural Networks (ICANN 2013), September 2013.

Sami Keronen, \textbf{Kyunghyun Cho}, Tapani Raiko, Alexander Ilin
and Kalle Palom\"aki. Gaussian-Bernoulli Restricted Boltzmann
Machines and Automatic Feature Extraction for Noise Robust
Missing Data Mask Estimation. In Proceedings of the 38th
International Conference on Acoustics, Speech, and Signal
Processing (ICASSP 2013), May 2013.




\section{Other Non-Referred Publications}

Tapani Raiko, \textbf{Kyunghyun Cho} and Alexander Ilin.
Derivations of the Enhanced Gradient for the Boltzmann
Machine.  Technical Report. Aalto University, 2011.

Tapani Raiko, \textbf{Kyunghyun Cho} and Alexander Ilin.
Enhanced Gradient for Learning Boltzmann Machines.
In the Learning Workshop. Fort Lauderdale, Florida. April
2011. (abstract only)

\textbf{Kyunghyun Cho}, Tapani Raiko and Juha Karhunen.
Advances in Training Restricted Boltzmann Machines.
In the 11th International Symposium on Intelligent Data
Analysis (IDA 2012). Helsinki, Finland. Oct 2012. (abstract
only)












\end{document}




